### 2017-12-28 icde/revision/sec-incAlg.tex

Let $G_A=(V_A,E_A)$, $G_B=(V_B,E_B)$ and $G_C=(V_C,E_C)$, respectively, and
let $E_{AB}$ and $E_{CB}$  be the sets of edges from $G_A$ to $G_B$ and from $G_C$ to $G_B$, respectively.
In this way, graph $G^+$ is divided into subgraphs $\{G_A$, $G_B$, $G_C\}$ and edge sets $\{E_{AB}, E_{CB}\}$.
%
We then have $G_C$ = $G^+[\Delta V]$, $\Delta E$ = $E_C\cup E_{CB}$, $V$ = $V_A\cup V_B$ and $E$ = $E_A\cup E_B\cup E_{AB}$.

@@

Observe that (a) a topological order of $G'_C$ can be computed in $O(|V_C|+|E_C|+|E_{CB}|)$ time,
(b) updating the TWPageRank scores of nodes in subgraphs $G_B$ and $G_C$ costs $O(|V_B\cup V_C|+|E_{B,a}\cup E_{C,a}\cup E_{CB}|)+t^+|E_{B,i}\cup E_{C,i}|)$ time, and, finally, (c) updating the scores of nodes in $G_A$ costs $O(|V_A|)$ time. From these, the following holds.

\begin{prop} \label{lemma-inc-citation-comp}
Given an update $\Delta$ = $\Delta V\cup\Delta E$ of citation or venue graph $G(V,E)$, the TWPageRank vector of $G$ and the topological order of $G'$, algorithm \inctwprscc runs in $O(|V\cup \Delta V| + |E_B\cup E_C\cup E_{CB}| + t^+|E_{B,i}\cup E_{C,i}|)$ time.
\end{prop}

@@

By Propositions~\ref{prop-converg} \& \ref{lemma-inc-topo} and Theorem \ref{lemma-subgraphA}, one can easily verify the correctness of algorithm \inctwprscc.
%
Note that  (a) algorithm \inctwprscc computes \sccs and derives the topological order based  on $\Delta$ only, instead of $G^{+}$,
(b) it skips edges in $E_A\cup E_{AB}$ when updating the scores of nodes in $G_A$ and $G_B$, and
(c) the number $t^+$ is very likely smaller than the number $t$ of \twprscc when updating scores of nodes in $G_B$.
%
All these make \inctwprscc faster than \twprscc even though they have very similar time complexity.
%, as will also been shown by the experimental study,

@@

\stitle{Time complexity analysis of the incremental algorithm}.
By the analyses above, the time complexity of \incensemble is the same as \batensemble, except that \incensemble saves $O(|E^c_A\cup E^c_{AB}|)$ and $O(|E^v_A\cup E^v_{AB}|)$ time on the updated citation and venue graphs at an extra space cost for the affected/unaffected areas and the original edge weights.

Despite of its similar time complexity to \batensemble, algorithm \incensemble typically achieves a substantial efficiency improvement over \batensemble, according to our statistics of affected/unaffected areas given a yearly update, \ie articles of 2011 on \aan and 2015 on \aminer and \magdata, respectively, shown in Table~II.
%
(a) It saves $O(|V^c|+|E^c|)$ and $O(|V^v|+|E^v|)$ time when maintaining \sccs and the topological order based on $\Delta^c$ and $\Delta^v$ only, where ($|V^c|$, $|E^c|$, $|V^v|$, $|E^v|$) are more than (92\%, 89\%, 93\%, 89\%) of ($|V^{c,+}|$, $|E^{c,+}|$, $|V^{v,+}|$, $|E^{v,+}|$) on all tested graphs;
(b) It saves $O(|E^c_A \cup E^c_{AB}|)$ time when updating scores on $V^c$, where edges in $E^c_A\cup E^c_{AB}$ account for more than 28\% of total edges;
(c) It saves $O(|E^c|)$ time when computing popularity of articles, which accounts for more than 89\% of $|E^{c,+}|$;
And, finally, (d) It is likely to compute TWPageRank scores on $V^c_B$ and $V^v_B$ with less iterations.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[tb!]
%\vspace{-2ex}
\begin{center}
\caption{\small Statistics of affected/unaffected areas}
\label{tab-inc}
%\begin{small}
\vspace{-.5ex}
\eat{
\begin{tabular}{|c|c|c|}
\hline
{\bf Graphs} & $|V_A|$\hspace{2ex}$|V_B|$\hspace{3ex}$|V_C|$ & $|E_A|$\hspace{2ex}$|E_{AB}|$\hspace{2ex}$|E_B|$\hspace{2ex}$|E_{CB}|$\hspace{2ex}$|E_C|$ \\
\hline \hline
% citation graphs
\aan & $46.9\%$\ $47.3\%$\ $5.8\%$ & \ $2.9\%$\ $25.9\%$\ $60.5\%$\ $10.4\%$ \hspace{1ex} $0.3\%$ \\
\aminer & $81.4\%$ \hspace{1ex} $10.7\%$ \hspace{1ex} $7.8\%$ & $18.0\%$ \hspace{1ex} $53.2\%$ \hspace{1ex} $25.1\%$ \hspace{1ex} \ $2.3\%$ \hspace{1ex} $1.4\%$ \\
\magdata & $69.5\%$ \hspace{1ex} $25.9\%$ \hspace{1ex} $4.5\%$ & \ $1.0\%$ \hspace{1ex} $27.4\%$ \hspace{1ex} $64.5\%$ \hspace{1ex} \ $7.0\%$ \hspace{1ex} $0.1\%$ \\ \hline
% venue graphs
\aan & \ $2.1\%$ \hspace{1ex} $92.0\%$ \hspace{1ex} $5.8\%$ & \ $1.0\%$ \hspace{1ex} \ $1.0\%$ \hspace{1ex} $88.8\%$ \hspace{1ex} $10.0\%$ \hspace{1ex} $0.2\%$ \\
\aminer & $45.8\%$ \hspace{1ex} $47.7\%$ \hspace{1ex} $6.4\%$ & \ $0.0\%$ \hspace{1ex} \ $3.2\%$ \hspace{1ex} $95.4\%$ \hspace{1ex} \ $1.0\%$ \hspace{1ex} $0.1\%$ \\
\magdata & $12.4\%$ \hspace{1ex} $84.6\%$ \hspace{1ex} $3.0\%$ & \ $0.0\%$ \hspace{1ex} \ $0.1\%$ \hspace{1ex} $92.6\%$ \hspace{1ex} \ $7.1\%$ \hspace{1ex} $0.1\%$ \\
 \hline
\end{tabular}
}
\begin{tabular}{|c|c c c|c c c|}
\hline
 & \multicolumn{3}{c|}{\bf Citation graphs on}   & \multicolumn{3}{c|}{\bf Venue graphs on}    \\
\raisebox{1ex}[0pt]{\bf Statis.} & \aan & \aminer & \magdata & \aan & \aminer & \magdata \\
\hline \hline
$|V_A|$ & 47.4\% & 52.3\% & 69.2\% & 2.1\% & 8.7\% & 12.4\% \\
$|V_B|$ & 46.8\% & 40.0\% & 26.3\% & 92.0\% & 84.8\% & 84.6\% \\
$|V_C|$ & \ 5.8\% & \ 7.8\% & \ 4.5\% & \ 5.8\% & \ 6.4\% & \ 3.0\% \\ \hline
% venue graphs
$|E_A|$ & \ 3.0\% & 2.4\% & \ 0.9\% & \ 0.0\% & \ 0.0\% & \ 0.0\% \\
$|E_{AB}|$ & 26.5\% & 30.2\% & 26.6\% & \ 1.2\% & \ 0.2\% & \ 0.1\% \\
$|E_B|$ & 59.8\% & 59.3\% & 65.5\% & 88.6\% & 92.3\% & 92.6\% \\
$|E_{CB}|$ & 10.4\% & \ 7.2\% & \ 7.0\% & 10.0\% & \ 7.3\% & \ 7.1\% \\
$|E_C|$ & \ 0.3\% & \ 0.9\% & \ 0.1\% & \ 0.2\% & \ 0.2\% & \ 0.1\% \\ \hline
\end{tabular}
%\end{small}
\end{center}
\vspace{-5ex}
\end{table}
%%%%%%%%%%%%%%%%%%%

>>>>

Let $G_A=(V_A,E_A)$, $G_B=(V_B,E_B)$ and $G_C=(V_C,E_C)$, respectively, and
let $E_{AB}$ and $E_{CB}$  be the sets of edges from $G_A$ to $G_B$ and from $G_C$ to $G_B$, respectively.
In this way, graph $G^+$ is divided into subgraphs $\{G_A$, $G_B$, $G_C\}$ and edge sets $\{E_{AB}, E_{CB}\}$.
%
We then have $G^+[\Delta V]$ = $G_C$, $\Delta E$ = $E_C\cup E_{CB}$, $V$ = $V_A\cup V_B$ and $E$ = $E_A\cup E_B\cup E_{AB}$.

@@

Observe that (a) a topological order of the block-wise graph of $G_C$ can be computed in $O(|\Delta V|+|\Delta E|)$ time,
(b) updating the TWPageRank scores of nodes in $V_B$ and $V_C$ costs $O(|V_B\cup V_C|+|E_{B,a}\cup E_{C,a}\cup E_{CB}|)+t^+|E_{B,i}\cup E_{C,i}|)$ time, where $t^+$ is  the maximum number of iterations among all \sccs in $G_B$ and $G_C$, and, finally, (c) updating the scores of nodes in $V_A$ costs $O(|V_A|)$ time. From these, the following holds.

\begin{prop} \label{lemma-inc-citation-comp}
Given an update $\Delta$ = $\Delta V\cup\Delta E$ of citation or venue graph $G(V,E)$, the TWPageRank vector of $G$ and the topological order of $G'$, algorithm \inctwprscc runs in $O(|V\cup \Delta V| + |E_{B,a}\cup \Delta E| + t^+|E_{B,i}\cup E_{C,i}|)$ time.
\end{prop}

@@

By Propositions~\ref{prop-converg} \& \ref{lemma-inc-topo} and Theorem \ref{lemma-subgraphA}, one can easily verify the correctness of algorithm \inctwprscc.
%
Note that  (a) algorithm \inctwprscc computes \sccs and derives the topological order based  on $\Delta$ only, instead of $G^{+}$,
(b) it skips edges in $E_A\cup E_{AB}$ when updating the scores of nodes in $V_A$ and $V_B$, and
(c) the number $t^+$ is very likely smaller than the number $t$ of \twprscc when updating scores of nodes in $V_B$.
%
All these make \inctwprscc faster than \twprscc even though they have very similar time complexity.
%, as will also been shown by the experimental study,

@@

\stitle{Time complexity analysis of the incremental algorithm}.
By the analyses above, the time complexity of \incensemble is the same as \batensemble, except that \incensemble saves $O(|E^c_A\cup E^c_{AB}|)$ and $O(|E^v_A\cup E^v_{AB}|)$ time when computing TWPageRank  on the updated citation and venue graphs at an extra space cost for the affected/unaffected division and the copy of original edge weights.

Despite of its similar time complexity to \batensemble, algorithm \incensemble typically achieves a substantial efficiency improvement over \batensemble, according to our statistics of affected/unaffected areas given a yearly update, \ie articles of 2011 on \aan and 2015 on \aminer and \magdata, respectively, shown in Table~II.
%
(a) It saves $O(|V^c|+|E^c|)$ and $O(|V^v|+|E^v|)$ time when maintaining \sccs and the topological order based on the update data only, 
%where ($|V^c|$, $|E^c|$, $|V^v|$, $|E^v|$) are more than (92\%, 89\%, 93\%, 89\%) of ($|V^{c,+}|$, $|E^{c,+}|$, $|V^{v,+}|$, $|E^{v,+}|$) on all tested graphs;
where ($|V|$, $|E|$) are more than (92\%, 89\%) of ($|V^{+}|$, $|E^{+}|$) on all tested citation and venue graphs;
(b) It saves $O(|E^c_A \cup E^c_{AB}|)$ time when updating scores on $V^c$, where edges in $E^c_A\cup E^c_{AB}$ account for more than 28\% of total;
(c) It saves $O(|E^c|)$ time when computing popularity of articles, which accounts for more than 89\% of total;
And, finally, (d) It is likely to compute TWPageRank scores on $V^c_B$ and $V^v_B$ with less iterations.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[tb!]
%\vspace{-2ex}
\begin{center}
\caption{\small Statistics of affected/unaffected areas}
\label{tab-inc}
%\begin{small}
\vspace{-.5ex}
\eat{
\begin{tabular}{|c|c|c|}
\hline
{\bf Graphs} & $|V_A|$\hspace{2ex}$|V_B|$\hspace{3ex}$|V_C|$ & $|E_A|$\hspace{2ex}$|E_{AB}|$\hspace{2ex}$|E_B|$\hspace{2ex}$|E_{CB}|$\hspace{2ex}$|E_C|$ \\
\hline \hline
% citation graphs
\aan & $46.9\%$\ $47.3\%$\ $5.8\%$ & \ $2.9\%$\ $25.9\%$\ $60.5\%$\ $10.4\%$ \hspace{1ex} $0.3\%$ \\
\aminer & $81.4\%$ \hspace{1ex} $10.7\%$ \hspace{1ex} $7.8\%$ & $18.0\%$ \hspace{1ex} $53.2\%$ \hspace{1ex} $25.1\%$ \hspace{1ex} \ $2.3\%$ \hspace{1ex} $1.4\%$ \\
\magdata & $69.5\%$ \hspace{1ex} $25.9\%$ \hspace{1ex} $4.5\%$ & \ $1.0\%$ \hspace{1ex} $27.4\%$ \hspace{1ex} $64.5\%$ \hspace{1ex} \ $7.0\%$ \hspace{1ex} $0.1\%$ \\ \hline
% venue graphs
\aan & \ $2.1\%$ \hspace{1ex} $92.0\%$ \hspace{1ex} $5.8\%$ & \ $1.0\%$ \hspace{1ex} \ $1.0\%$ \hspace{1ex} $88.8\%$ \hspace{1ex} $10.0\%$ \hspace{1ex} $0.2\%$ \\
\aminer & $45.8\%$ \hspace{1ex} $47.7\%$ \hspace{1ex} $6.4\%$ & \ $0.0\%$ \hspace{1ex} \ $3.2\%$ \hspace{1ex} $95.4\%$ \hspace{1ex} \ $1.0\%$ \hspace{1ex} $0.1\%$ \\
\magdata & $12.4\%$ \hspace{1ex} $84.6\%$ \hspace{1ex} $3.0\%$ & \ $0.0\%$ \hspace{1ex} \ $0.1\%$ \hspace{1ex} $92.6\%$ \hspace{1ex} \ $7.1\%$ \hspace{1ex} $0.1\%$ \\
 \hline
\end{tabular}
}
\begin{tabular}{|c|c c c|c c c|}
\hline
 & \multicolumn{3}{c|}{\bf Citation graphs on}   & \multicolumn{3}{c|}{\bf Venue graphs on}    \\
\raisebox{1ex}[0pt]{\bf Statis.} & \aan & \aminer & \magdata & \aan & \aminer & \magdata \\
\hline \hline
$|V_A|$ & 47.4\% & 52.3\% & 69.2\% & 2.1\% & 8.7\% & 12.4\% \\
$|V_B|$ & 46.8\% & 40.0\% & 26.3\% & 92.0\% & 84.8\% & 84.6\% \\ 
$|V_C|$ & \ 5.8\% & \ 7.8\% & \ 4.5\% & \ 5.8\% & \ 6.4\% & \ 3.0\% \\ \hline
$|E_A|$ & \ 3.0\% & 2.4\% & \ 0.9\% & \ 0.0\% & \ 0.0\% & \ 0.0\% \\
$|E_{AB}|$ & 26.5\% & 30.2\% & 26.6\% & \ 1.2\% & \ 0.2\% & \ 0.1\% \\
$|E_B|$ & 59.8\% & 59.3\% & 65.5\% & 88.6\% & 92.3\% & 92.6\% \\ 
$|E_{CB}|$ & 10.4\% & \ 7.2\% & \ 7.0\% & 10.0\% & \ 7.3\% & \ 7.1\% \\
$|E_C|$ & \ 0.3\% & \ 0.9\% & \ 0.1\% & \ 0.2\% & \ 0.2\% & \ 0.1\% \\ \hline
\end{tabular}
%\end{small}
\end{center}
\vspace{-5ex}
\end{table}
%%%%%%%%%%%%%%%%%%%
